### 2020-03-17 paper/main.tex
added code and more citations

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pslatex}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{paralist}
\usepackage[utf8]{inputenc}
\usepackage{multicol} 
\usepackage[hidelinks]{hyperref}
\usepackage{nameref}

@@

As time-series datasets become ever more popular, the need for deep learning models becomes that much greater.
In our black-box model, we analyze deep learning models such as Convolutional Neural Networks, which have become increasingly popular and widely used in the last decade. However, their complex nature results in a lack of understanding of its inner workings \cite{wang_hybrid_2019}.
As the use and complexity of black-box models rises, so too does the need for an interpretable accessory. For this reason, we propose a hybrid model consisting of a black-box for classification and an interpretable white-box which highlights characteristics of a time series for users to understand.

@@

We analyzed our model on three radio signal datasets, which we will refer to as dataset A, B, and C throughout this thesis. These datasets were generated through Spatial Modulation which is a transmission technique that uses multiple antennae which maps a block of information bits to two units, a symbol chosen from a constellation diagram, and a unique transmit antenna number that is chosen from a set of transmit antennae \cite{mesleh_spatial_2008}. The method in which transmit antennae send and receive radio waves can be described through polarization. Two popular basis polarizations are horizontal linear, H, and vertical linear, V. Our datasets contain data horizontally transmitted and vertically received (HV), as well as data vertically transmitted and vertically received (VV).

@@

\subsection{Short-Time Fourier Transform}
% [stft]
The Short-Time Fourier transform (STFT) is a Fourier related transform used to determine the sinusoidal frequency and phase content of local sections of a signal as it changes over time \cite{hill_uncertainty_nodate}.
Computing STFT requires the signal to be divided into segments of equal length and then have the FT applied to that segment. This allows us to view the Fourier spectrum at a more granular level, which could potentially reveal different patterns amongst signals of different classes.

@@

Wavelet transforms are similar to the FT in that they deconstruct a signal using representations of other signals. The key difference is that wavelet signals are finite in time and frequency as opposed to sine and cosine signals, which can carry on indefinitely \cite{strang_wavelets_1996}. This allows us to extract information from a signal with respect to time and location.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.4]{../media/wavelet_families.png}
   \end{center}
   \caption{Example of different types of wavelets  \cite{strang_wavelets_1996}.}
   \label{fig:reinforcementAgent}
\end{figure}

A signal is analyzed using different versions of dilated and translated basis functions called the mother wavelet  \cite{strang_wavelets_1996}. There are two types of wavelet transformations, discrete and continuous. In this thesis, we focus on discrete wavelet transformations, which use a discrete set of wavelet scales and translations to decompose the signal into a mutually orthogonal set of wavelets.

@@

We use spline interpolation to resize each level of decomposition into a single array. We tested different sizes of interpolation from N to N/3, where N is the size of the largest discrete signal size, and found no reduction in performance.

@@

Convolutional Neural Networks perform feature learning via non-linear transformations implemented as a series of layers. The input data is a multidimensional array, called a tensor. The tensor is passed through an input layer, followed by a series of hidden layers to extract features, and an output layer, which in the case of classification, gives a probability for each class.

% create your own design
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.3]{../media/nn_highlight.jpeg}
   \end{center}
   \caption{Example of a Convolutional Neural Network \cite{yamashita_convolutional_2018}.}
   \label{fig:cnn_example}
\end{figure}

@@

% [multimodal]
Due to the superior performance and computationally tractable representation capability in multiple domains such as visual, audio, and text, deep neural networks have gained tremendous popularity in multimodal learning tasks \cite{kim_multimodal_2018}. Typically, domain-specific neural networks are used on different modalities to generate their representations, and the individual representations are merged or aggregated \cite{kim_multimodal_2018}. Finally, the prediction is made on top of aggregated representation, usually with another neural network to capture the interactions between models and learn complex function mapping between input and output.

@@

\section{Dataset B}

@@

>>>>

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pslatex}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{paralist}
\usepackage[utf8]{inputenc}
\usepackage{multicol} 
\usepackage[hidelinks]{hyperref}
\usepackage{nameref}
\usepackage{setspace}
\usepackage{listings}

\usepackage[toc,page]{appendix}

@@

As time-series datasets become ever more popular, the need for deep learning models becomes that much greater. In our black-box model, we analyze deep learning models such as Convolutional Neural Networks, which have become increasingly popular and widely used in the last decade  \cite{cui_multi-scale_2016}. However, their complex nature results in a lack of understanding of its inner workings \cite{wang_hybrid_2019}.
As the use and complexity of black-box models rises, so too does the need for an interpretable accessory. For this reason, we propose a hybrid model consisting of a black-box for classification and an interpretable white-box which highlights characteristics of a time series for users to understand.

@@

We analyzed our model on three radio signal datasets, which we will refer to as dataset A, B, and C throughout this thesis. These datasets were generated through Spatial Modulation which is a transmission technique that uses multiple antennae which maps a block of information bits to two units, a symbol chosen from a constellation diagram, and a unique transmit antenna number that is chosen from a set of transmit antennae \cite{mesleh_spatial_2008}. The method in which transmit antennae send and receive radio waves can be described through polarization. Two popular basis polarizations are horizontal linear, H, and vertical linear, V \cite{oshea_convolutional_2016}. Our datasets contain data horizontally transmitted and vertically received (HV), as well as data vertically transmitted and vertically received (VV).

@@

\subsection{Short-Time Fourier Transform}
% [stft]
The Short-Time Fourier transform (STFT) is a Fourier related transform used to determine the sinusoidal frequency and phase content of local sections of a signal as it changes over time \cite{hill_uncertainty_nodate}.
Computing STFT requires the signal to be divided into segments of equal length and then have the FT applied to that segment \cite{allen_unified_1977}. This allows us to view the Fourier spectrum at a more granular level, which could potentially reveal different patterns amongst signals of different classes.

@@

Wavelet transforms are similar to the FT in that they deconstruct a signal using representations of other signals \cite{misiti_wavelets_2013}. The key difference is that wavelet signals are finite in time and frequency as opposed to sine and cosine signals, which can carry on indefinitely \cite{strang_wavelets_1996}. This allows us to extract information from a signal with respect to time and location.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.4]{../media/wavelet_families.png}
   \end{center}
   \caption{Example of different types of wavelets \cite{lopez_development_2017}.}
   \label{fig:reinforcementAgent}
\end{figure}

A signal is analyzed using different versions of dilated and translated basis functions called the mother wavelet  \cite{strang_wavelets_1996}. There are two types of wavelet transformations, discrete and continuous \cite{imani_curve_2016}. In this thesis, we focus on discrete wavelet transformations, which use a discrete set of wavelet scales and translations to decompose the signal into a mutually orthogonal set of wavelets.

@@

We use spline interpolation to resize each level of decomposition into a single array because it allows to retain properties of our original data even in a higher dimension \cite{gregory_shape_1985}. We tested different sizes of interpolation from N to N/3, where N is the size of the largest discrete signal size, and found no reduction in performance.

@@

Convolutional Neural Networks perform feature learning via non-linear transformations implemented as a series of layers \cite{aqib_smarter_2019}. The input data is a multidimensional array, called a tensor. The tensor is passed through an input layer, followed by a series of hidden layers to extract features, and an output layer, which in the case of classification, gives a probability for each class.

% create your own design
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/cnn_example.png}
   \end{center}
   \caption{Example of a Convolutional Neural Network \cite{alom_state---art_2019}.}
   \label{fig:cnn_example}
\end{figure}

@@

% [multimodal]
Due to the superior performance and computationally tractable representation capability in multiple domains such as visual, audio, and text, deep neural networks have gained tremendous popularity in multimodal learning tasks \cite{kim_multimodal_2018}. Typically, domain-specific neural networks are used on different modalities to generate their representations, and the individual representations are merged or aggregated \cite{liu_learn_2018}. Finally, the prediction is made on top of aggregated representation, usually with another neural network to capture the interactions between models and learn complex function mapping between input and output.

@@

\section{Dataset C}

@@

\begin{appendices}
   \chapter{MTF Code}
      \section{Main File}
         \lstinputlisting[language=Python,  basicstyle=\small, columns=fullflexible ]{../code/mtf/main.py}
      \section{Calculating MTF}
         \lstinputlisting[language=Python,  basicstyle=\small, columns=fullflexible]{../code/mtf/complex_signal.py}
      \section{Helper functions}
         \lstinputlisting[language=Python,  basicstyle=\small, columns=fullflexible]{../code/mtf/util.py}
   \chapter{Hybrid Model Code}
      \section{Main File}
         \lstinputlisting[language=Python,  basicstyle=\small, columns=fullflexible]{../code/hybrid_model/main.py}
      \section{White-Box Model}
         \lstinputlisting[language=Python,  basicstyle=\small, columns=fullflexible]{../code/hybrid_model/white_box.py}
      \section{Black-Box Model}
         \lstinputlisting[language=Python,  basicstyle=\small, columns=fullflexible]{../code/hybrid_model/black_box.py}

\end{appendices}
